---
title: "SNP Count"
output: html_document
---

```{r setup, include=FALSE}
library("dplyr")
library("ggplot2")
library("RColorBrewer")
library("reshape2")
library("plotly")
```

## SNP Count for 8 different populations
```{r count_plot, warning=FALSE,echo=FALSE, fig.height=8, fig.width=11}
count_file <- read.csv("SNP_count_pooled_samples.txt", sep = "\t", header = FALSE)
colnames(count_file) <- c("Population","Count")
options(scipen=999)
bar_graph <- ggplot(data = count_file, aes(x=Population,y=Count,fill = Population))+
  geom_bar(stat="identity")+
  geom_text(label = count_file$Count, size=4)+
  xlab("Population")+
  ylab("Number of SNPs")+
  scale_fill_brewer(palette="Dark2")+
  theme_minimal()
ggplotly(bar_graph)
```

## Stacked bar graph of the number of snps across populations in each chromosome.
```{r window_plot, warning=FALSE,echo=FALSE, fig.height=8, fig.width=11}
window_file <- read.csv("window_count.txt", sep = "\t", header = FALSE)
colnames(window_file) <- c("Population","Chromosome","Window","Count")
options(scipen=999)
bar_graph_window <- ggplot(data = window_file, aes(x=Chromosome,y=Count,fill = Population))+
  geom_bar(stat="identity")+
  xlab("Chromosome")+
  ylab("Number of SNPs")+
  scale_fill_brewer(palette="Dark2")+
  theme_minimal()
ggplotly(bar_graph_window)
```

## Clustered bar graph of the number of snps across populations in each chromosome (Same plot as before but easier to compare between population).

```{r chromosome_comparison_plot, warning=FALSE,echo=FALSE, fig.height=8, fig.width=11}
chromosome_comparison_plot <- ggplot(data = window_file, aes(x=Chromosome,y=Count,fill = Population))+
  geom_bar(position="dodge",stat="identity")+
  xlab("Chromosome")+
  ylab("Number of SNPs")+
  scale_fill_brewer(palette="Dark2")+
  theme_minimal()
ggplotly(chromosome_comparison_plot)
```

## Line Graph representing the number of SNPs in 100kB window: 

### Chromosome X:

```{r X_chromosome , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
X_chromosome <- ggplot(data = window_file[window_file$Chromosome==" ChLGX ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome X")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,9000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(X_chromosome)

```

### Chromosome 2:

```{r Chromosome_two , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_two <- ggplot(data = window_file[window_file$Chromosome==" ChLG2 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 2")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,16000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_two)

```

### Chromosome 3:

```{r Chromosome_three , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_three <- ggplot(data = window_file[window_file$Chromosome==" ChLG3 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 3")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,32000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_three)

```

### Chromosome 4:

```{r Chromosome_four , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_four <- ggplot(data = window_file[window_file$Chromosome==" ChLG4 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 4")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,13000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_four)

```

### Chromosome 5:

```{r Chromosome_five , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_five <- ggplot(data = window_file[window_file$Chromosome==" ChLG5 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 5")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,16000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_five)

```

### Chromosome 6:

```{r Chromosome_six , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_six <- ggplot(data = window_file[window_file$Chromosome==" ChLG6 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 6")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,11000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_six)

```

### Chromosome 7:

```{r Chromosome_seven , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_seven <- ggplot(data = window_file[window_file$Chromosome==" ChLG7 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 7")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,17000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_seven)

```

### Chromosome 8:

```{r Chromosome_eight , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_eight <- ggplot(data = window_file[window_file$Chromosome==" ChLG8 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 8")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,15000000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_eight)

```

### Chromosome 9:

```{r Chromosome_nine , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_nine <- ggplot(data = window_file[window_file$Chromosome==" ChLG9 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 9")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,16500000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_nine)

```

### Chromosome 10:

```{r Chromosome_ten , warning=FALSE,echo=FALSE, fig.height=11, fig.width=16}
Chromosome_ten <- ggplot(data = window_file[window_file$Chromosome==" ChLG10 ",], aes(x=Window,y=Count,color = Population))+
  geom_line(stat="identity")+
  xlab("100kb window")+
  ylab("Count")+
  ggtitle("Chromosome 10")+
  theme_light()+
  scale_x_continuous(breaks = seq(0,7300000,100000))+
  theme(axis.text.x = element_blank())
ggplotly(Chromosome_ten)

```